\textbf{Broadridge Financial Solutions, Bangalore, India} \hfill Jun 2021 -- Dec 2023\\
\textit{Associate Software Engineer}\\
\begin{itemize}
  \item Built and maintained automated QA frameworks using \textbf{Java, Selenium, Groovy, and TestNG}, improving test coverage and execution efficiency.
  \item Developed and optimized \textbf{Python scripts} for log parsing, QA data automation, and validation to streamline testing workflows.
  \item Designed and managed \textbf{SQL and MongoDB} test data to support end-to-end validation and integration testing.
  \item Performed database and data integration validation (including Excel-based checks) to ensure accuracy and consistency across pipelines.
  \item Conducted cloud-based testing on \textbf{AWS} to validate distributed systems and cloud-hosted applications.
  \item Integrated automated test cycles into \textbf{CI/CD pipelines} to improve release quality and reduce deployment timelines.
  \item Worked in Agile delivery using \textbf{Jira} for defect tracking, sprint planning, and cross-team collaboration.
\end{itemize}

\textbf{IBM, Bangalore, India} \hfill Jan 2021 -- May 2021\\
\textit{Quality Engineer (EMR Project)}\\
\begin{itemize}
  \item Designed, reviewed, and executed detailed test scenarios and test cases to ensure comprehensive software validation.
  \item Analyzed SRS documents and defined test scenarios to support structured test planning and execution.
  \item Maintained \textbf{Requirement Traceability Matrices (RTM)} to ensure full requirement coverage.
  \item Executed functional and regression testing for EMR systems to improve reliability and release confidence.
  \item Performed data validation and documentation to support audit readiness and knowledge transfer.
  \item Collaborated with developers to track, troubleshoot, and resolve defects, improving product quality and timelines.
\end{itemize}

\textbf{LOTUS Hospital, Bangalore, India} \hfill Sep 2020 -- Dec 2020\\
\textit{Manual Testing Engineer}\\
\begin{itemize}
  \item Supported development of a patient data management system and a neonatal ICU dashboard with educational resources.
  \item Executed manual testing (functional, regression, cross-browser) including iOS validation to ensure strong user experience.
  \item Created test plans, scenarios, and cases; participated in defect triage and collaborated with QA leads to resolve issues.
\end{itemize}
